Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-02 manuscript.qmd
Built site for gh-pages

![Comparison of the computed and observed prevalences for scenarios that illustrate the model's capability of accounting for the correlation between ipsi- and contralateral involvement. We show three scenarios where we consider the joint involvement of contralateral LNL II together with different ipsilateral involvements: 1) the ipsilateral neck shows no involvement in blue (LNLs I to V are healthy, LNL VII is unspecified because data on it is missing for some patients), 2) where ipsilateral LNL II is involved in orange (LNLs I, III, IV, and V are healthy), and 3) where ipsilateral LNLs II and III are involved in orange (LNLs I, IV, and V are healthy). These two scenarios are plotted for all combinations of T-category (early in top row, advanced in bottom row) and tumor lateralization (lateralized in left column, extending over mid-sagittal line in the right column).](figures/fig_model_prevalences_with_ipsi.svg){#fig-model-prevalences-with-ipsi}

>>>>

![Comparison of the computed and observed prevalences for scenarios that illustrate the model's capability of accounting for the correlation between ipsi- and contralateral involvement. We show three scenarios where we consider the joint involvement of contralateral LNL II together with different ipsilateral involvements: 1) the ipsilateral neck shows no involvement in green (LNLs I to V are healthy, LNL VII is unspecified because data on it is missing for some patients), 2) where ipsilateral LNL II is involved in orange (LNLs I, III, IV, and V are healthy), and 3) where ipsilateral LNLs II and III are involved in red (LNLs I, IV, and V are healthy). These three scenarios are plotted for all combinations of T-category (early in top row, advanced in bottom row) and tumor lateralization (lateralized in left column, extending over mid-sagittal line in the right column).](figures/fig_model_prevalences_with_ipsi.svg){#fig-model-prevalences-with-ipsi}
